Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-11-02 Scripts/Initial_Analysis.Rmd
Included the sf fix. and commented the weighted method of figure 3

@@

##### Fig. 1. Accumulative plots

@@

# Per EEZs
Eez_d_hist <- Eme_Res %>% 
  group_by(eezid,sau_fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  # filter(metric != "n_taxa") %>% 
  mutate(
    reverse = abs(value-2100)  + 2000
  )

@@

  map <- ggplot(toe_map_data) +
    geom_sf(
      aes(
        fill = reverse #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            # aes(fill = participation+2000), #original map
            aes(fill = participation),
            color =  "white",
            size = 0.1
    ) +
    # grey maps
    # ggplot() +
    geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +
    # geom_sf(data = grey_eez, aes(), fill = "white", color =  "grey50",size = 0.1) +
    geom_sf(data = no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text",
             x =-150,
             y = -69,
             label = "Transboundary fishing revenue (%)",
             color="black",
             size=5,
             angle=0,
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-72,-35,5,46,82),
             y = -69,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set ToE labels
    annotate("text", 
             x =-150,
             y = -85,
             label = "Average year of range shift",
             color="black", 
             size=5, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-79,-39,2,42,81),
             y = -85,
             # label = seq(2100,2000,-25), # original
             label = c(">2100",seq(2075,2000,-25)), # not inluding the > because we dont know
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set No emergence label
    annotate("text",
             x =110,
             y = -77,
             label = "No shift",
             color="black",
             size=5,
             angle=0,
             fontface="bold",
             hjust=0) +
    scale_fill_viridis("",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       labels = c("","","","","")#,
                       # direction = -1
    ) +
    # scale_fill_gradientn("",
    #                      limits = c(2000,2100),
    #                      breaks = seq(2000,2100,25),
    #                       labels = c("","","","",""),
    #                      colours = pal
    # ) +
    # geom_hline(yintercept = c(-50,0,50,80)) +
    my_ggtheme_m() +
    theme(
      legend.box.margin = margin(t = -62, l = 252),
      legend.text = element_blank(),
      legend.key.width = unit(5, "line")
    )

@@

  # Weighted verion
  boxplot_data <- Eme_Res %>% 
    # Get the order of boxes
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>%
    group_by(un_sub_region) %>%
    summarise(n_eezs = length(unique(sf_eez_name))) %>%
    # Get the rest of the data
    left_join(Eme_Res) %>%
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>%
    # mutate(weight = )
    mutate(un_sub_region = ifelse(str_detect(un_sub_region,"Latin"),"Ltn. Ame. and\nthe Car.",
                                  ifelse(str_detect(un_sub_region,"Australia"),"Aus. and New Z.",
                                         ifelse(str_detect(un_sub_region,"Sub-Saharan"),"Sub-Saharan\nAfrica",
                                                paste(un_sub_region)))
    )#,
    # For number labels
    # un_sub_region = paste(un_sub_region," (n = ",n_eezs,")",sep="")
    )

@@

  # boxplot_data <- Eme_Res %>% 
  #   # Get the order of boxes
  #   filter(tresh == tresh_list[i],
  #          !is.na(un_sub_region)) %>%
  #   group_by(un_sub_region) %>% 
  #   summarise(order = median(emerging_yr),
  #             n_eezs = length(unique(sf_eez_name))) %>% 
  #   # Get the rest of the data
  #   left_join(Eme_Res) %>% 
  #   filter(tresh == tresh_list[i],
  #          !is.na(un_sub_region)) %>% 
  #   mutate(un_sub_region = ifelse(str_detect(un_sub_region,"Latin"),"Ltn. Ame. and\nthe Car.",
  #                                 ifelse(str_detect(un_sub_region,"Australia"),"Aus. and New Z.",
  #                                        ifelse(str_detect(un_sub_region,"Sub-Saharan"),"Sub-Saharan\nAfrica",
  #                                               paste(un_sub_region)))
  #   ),
  #   # For number labels
  #   un_sub_region = paste(un_sub_region," (n = ",n_eezs,")",sep="")
  #   )

>>>>

# Fix new updates of sf package
sf::sf_use_s2(use_s2 = FALSE)

@@

##### Fig. 2. Accumulative plots

@@

# Per EEZs
Eez_d_hist <- Eme_Res %>% 
  group_by(eezid,sau_fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = median(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  # filter(metric != "n_taxa") %>% 
  mutate(
    reverse = abs(value-2100)  + 2000
  )

@@

  map <- ggplot(toe_map_data) +
    geom_sf(
      aes(
        fill = reverse #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            # aes(fill = participation+2000), #original map
            aes(fill = participation),
            color =  "white",
            size = 0.1
    ) +
    # grey maps
    # ggplot() +
    geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +
    # geom_sf(data = grey_eez, aes(), fill = "white", color =  "grey50",size = 0.1) +
    geom_sf(data = no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text",
             x =-150,
             y = -69,
             label = "Transboundary fishing revenue (%)",
             color="black",
             size=5,
             angle=0,
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-72,-35,5,46,82),
             y = -69,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set ToE labels
    annotate("text", 
             x =-150,
             y = -85,
             label = "Average year of range shift",
             color="black", 
             size=5, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-79,-39,2,42,81),
             y = -85,
             # label = seq(2100,2000,-25), # original
             label = c(">2100",seq(2075,2000,-25)), # not inluding the > because we dont know
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set No emergence label
    annotate("text",
             x =110,
             y = -77,
             label = "No shift",
             color="black",
             size=5,
             angle=0,
             fontface="bold",
             hjust=0) +
    scale_fill_viridis("",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       labels = c("","","","","")#,
                       # direction = -1
    ) +
    # scale_fill_gradientn("",
    #                      limits = c(2000,2100),
    #                      breaks = seq(2000,2100,25),
    #                       labels = c("","","","",""),
    #                      colours = pal
    # ) +
    # geom_hline(yintercept = c(-50,0,50,80)) +
    my_ggtheme_m(leg_pos = "bottom") +
    theme(
      legend.box.margin = margin(t = -62, l = 252),
      legend.text = element_blank(),
      legend.key.width = unit(5, "line")
    )

@@

  # Weighted verion
  # boxplot_data <- Eme_Res %>% 
  #   # Get the order of boxes
  #   filter(tresh == tresh_list[i],
  #          !is.na(un_sub_region)) %>%
  #   group_by(un_sub_region) %>%
  #   summarise(n_eezs = length(unique(sf_eez_name))) %>%
  #   # Get the rest of the data
  #   left_join(Eme_Res) %>%
  #   filter(tresh == tresh_list[i],
  #          !is.na(un_sub_region)) %>%
  #   # mutate(weight = )
  #   mutate(un_sub_region = ifelse(str_detect(un_sub_region,"Latin"),"Ltn. Ame. and\nthe Car.",
  #                                 ifelse(str_detect(un_sub_region,"Australia"),"Aus. and New Z.",
  #                                        ifelse(str_detect(un_sub_region,"Sub-Saharan"),"Sub-Saharan\nAfrica",
  #                                               paste(un_sub_region)))
  #   )#,
  #   # For number labels
  #   # un_sub_region = paste(un_sub_region," (n = ",n_eezs,")",sep="")
  #   )

@@

  boxplot_data <- Eme_Res %>%
    # Get the order of boxes
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>%
    group_by(un_sub_region) %>%
    summarise(order = median(emerging_yr),
              n_eezs = length(unique(sf_eez_name))) %>%
    # Get the rest of the data
    left_join(Eme_Res) %>%
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>%
    mutate(un_sub_region = ifelse(str_detect(un_sub_region,"Latin"),"Ltn. Ame. and\nthe Car.",
                                  ifelse(str_detect(un_sub_region,"Australia"),"Aus. and New Z.",
                                         ifelse(str_detect(un_sub_region,"Sub-Saharan"),"Sub-Saharan\nAfrica",
                                                paste(un_sub_region)))
    ),
    # For number labels
    un_sub_region = paste(un_sub_region," (n = ",n_eezs,")",sep="")
    )
